---
title: "R Notebook"
author: akshay
date: 22/12/20
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
library(lfstat)
library(xts)
rep.row<-function(x,n){
   matrix(rep(x,each=n),nrow=n)
}
rep.col<-function(x,n){
   matrix(rep(x,each=n), ncol=n, byrow=TRUE)
}

spi_data <- read.csv("../cluster-3/spi_cluster3.csv")
#spi_data$date <- as.Date(spi_data$date, format = "%m/%d/%y")
spi_xts <- xts(spi_data[-1], order.by = as.Date(spi_data$date, format = "%Y-%m-%d"))
met_drought <- find_droughts(spi_xts, threshold = 0.0)
ic <- pool_ic(met_drought)
write.csv(ic, "../present/cluster-3/spi_pool.csv")
write.csv(summary(ic), "../cluster-3/spi_summary.csv")
#summary(ic)
#plot(ic) #, xaxt = "n")

sri_data = read.csv("../cluster-3/sri_cluster3.csv")
#sri_data$date <- as.Date(sri_data$date, format = "%Y-%m-%d")
#dates <- seq(as.Date("1966-01-01"), length=length(sri_data$date)*7, by="days")
sri_xts <- xts(sri_data[-1], order.by = as.Date(sri_data$date, format = "%Y-%m-%d"))
hydro_drought = find_droughts(sri_xts, threshold = 0.0)
ic <- pool_ic(hydro_drought)
write.csv(ic, "../cluster-3/sri_pool.csv")
write.csv(summary(ic), "../cluster-3/sri_summary.csv")
#summary(ic)
#plot(ic)#, rep.col(sri_data$date, 5))
```
```{r}
locations_df <- read.csv("../dataset/Discharge loctions Krishna Basin.csv") #SPI_station.csv
library(tidyverse)
library(ggmap)

locations <- as_tibble(locations_df)
library(sf)
library(mapview)
locations_sf <- st_as_sf(locations, coords = c("lon", "lat"), crs = 4326)
m = mapview(locations_sf)
mapshot(m, file = paste0(getwd(), "/map.png"), selfc)
mapshot(m, url = paste0(getwd(), "/map.html"))

```
```{r}
library(SCI)
PRECIP = read.csv("/media/akshay/New Volume/iiit_subjects/sem3/project_drought_prediction/data/weekly_runoff_bagalkot.csv")
spi.para <- fitSCI(PRECIP[,2],first.mon=1,time.scale=6,distr="gev",p0=TRUE)
spi <- transformSCI(PRECIP[,2],first.mon=1,obj=spi.para)
plot(date,spi,t="l")
```
Type any R code in the chunk, for example:


Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to built and preview an output.
